### 2019-05-27 Literature_Review/pages/review_content.tex
Changes; - Added more Literature review information - Moved papers - Added papers

\section{Research questions}

@@

\subsection{Topic conclusion}

@@

\section{Fingerprint representation schemes}
Another area of research is investigations into the actual physical encodings of the hash digest. This section will briefly discuss the current research available on the creation and security of actual encoding schemes. The actual details of the operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.

@@

\section{Topic conclusion}

@@

>>>>

\section{Possible research questions}

@@

\subsubsection{Topic conclusion}

@@

\subsection{Fingerprint representation schemes}
Another area of research is investigations into the actual physical encodings of the hash digest. This section will briefly discuss the current research available on the creation and security of actual encoding schemes. The actual details of the operation of the schemes are outside the scope of this literature review, therefore, minimal attention will be allocated to these details.

@@

\subsubsection{Topic conclusion}

@@

\section{Attacks on fingerprint verification}
This area of research studies ways to physically execute attacks on fingerprint encoding schemes. This differs from previously examined work due to papers discussing the performance and fallibility of encoding schemes simulated the attack without consideration for how the attack would be performed.

Research in this area is scant, with lots of research attention being directed towards the security of Man-in-the-Middle (MITM) attacks and not the encoding schemes themselves.

Research in 2002 by Konrad Rieck\cite{rieck2002fuzzy} is the first formalisation of attacks on fingerprint representations. The paper titled \textit{``Fuzzy Fingerprints Attacking Vulnerabilities in the Human Brain''}
aimed to look into ways users check hexadecimal encoded OpenSSH fingerprint representations. The author created an elegant way to `weight' more important chunks of the digest. The bytes furthest to the right and left of the digests provided the highest weight. The weight was the smallest in the centre of the digest. This provides a way to score digests and determine the best partial collisions found. For example with the target fingerprint: \verb|9F23| a partial match \verb|9313| is given a score of 45\% even though only two characters were matching. This is due to the weightings.

The paper contains an implementation with a ``1.2GHz CPU'' being able to obtain 130,000 H/s (With MD5). In comparison to this, a mid-range Intel i5-3320M CPU can today obtain 111,700,000 MD5 H/s shows that the results obtained from the paper are not applicable today. However, even with the low hash rate, the author was able to obtain some promising results. Figure~\ref{ref:fuzz} contains the best example used.

\begin{figure}[!h]
    \begin{center}
        \verb|TARGET: d6:b7:df:31:aa:55:d2:56:9b:32:71:61:24:08:44:87|
        \verb|MATCH:  d6:b7:8f:a6:fa:21:0c:0d:7d:0a:fb:9d:30:90:4a:87|
    \end{center}
    \caption{Best match obtained after a few minutes of hashing}
    \label{ref:fuzz}
\end{figure}

Overall the paper shows an interesting way to create partial fingerprint matches but is not quantified by any empirical evidence gathered on real world users. This, therefore, leaves gaps in the coverage of this literature.

The only other relevant research on this topic is the work by M 
Shirvanian \textit{et al.}\cite{shirvanian2014wiretapping} 
and their paper \textit{``Wiretapping via Mimicry: Short 
Voice Imitation Man-in-the-Middle Attacks on Crypto 
Phones''}. In this paper, the authors develop a way to 
impersonate users when authenticating 
Short-authentication-Strings (SAS) in pairing of 
Crypto-phones. To achieve this impersonating they propose 
two methods: ``Short voice reordering attack'' where an 
arbitrary SAS string is recreated by re-ordering snipped 
obtains from eavesdropping a previous connection
and ``Short voice morphing attacks'' whereby the use of 
previously eavesdropped audio snippets the attacker can
morph their own voice to match that of the victim. With 
these methods, they aimed to attack encodings of Numbers, 
PGP word list (previously discussed work by Juola and 
Zimmermann \cite{juola1996whole}) and MadLib (M. Goodrich 
\textit{et al.}\cite{goodrich2006loud} work also 
previously discussed). The effectiveness of these attacks 
were evaluated with a study involving 30 participants.

Results from the paper show the effectiveness of these 
methods. Compared to the baseline of the attacker's voice 
replacing the victim where this performed with a 
\textasciitilde18\% success rate. Morphing gained an 
overall success rate of 50.58\% and Reordering a very 
impressive 78.23\% success rate. Showing that these 
attacks provide an improvement on top of the naive implementation.

One of the biggest limitations addressed by the authors 
was the reduction in success rates as the size of the 
authentication string grew. The morphing and reordering 
attacks become increasingly ineffective as the user has 
longer to detect imperfections. This is not quantified by 
the author and the extent of this degradation is never 
empirically discussed. Therefore, the results from this 
study are only effective and applicable in a SAS context.

\subsubsection{Topic Conclusion}
Overall the literature for this subtopic remains sparse and incomplete. Further suggested work could look into the feasibility of generating partial collisions for all textual representations alongside quantified effectiveness on users. With the possibility to concentrate on a few selected implementations. The work would aim to focus on the various physical methods used and their feasibility. This is one area the previous literature has failed to cover and has only theoretically quantified attacker strength without consideration for the actual real-world cost of these attacks.

\section{Overall Summary}

\textbf{TODO: } Create an overall summary of all the gaps identified

### 2019-05-27 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - Added more Literature review information - Moved papers - Added papers

>>>>

\section{Wiretapping via Mimicry: Short Voice Imitation
Man-in-the-Middle Attacks on Crypto Phones}

The aim of the paper is to simulate a MITM attack on SAS and the voice channel used to authenticate

``Short voice reordering attack'' builds arbitrary SAS
strings in a victim’s voice by reordering previously eavesdropped SAS strings spoken by the victim.

called the ``short voice morphing attack;;, builds arbitrary SAS strings in a victim’s voice from a few previously eavesdropped sentences (less
than 3 minutes) spoken by the victim.

Is attempting to prove the assumption that "Mallory" being in control of the channel can controls Communications but cannot impersonate alice or bob.

Paper showed, that it is very possible to successfully attack SAS strings. Authors do comment on their difficulty in generating longer strings i.e. longer hash digests

Findings:
\begin{itemize}
    \item Success is more likely with shorter strings
    \item Showed that with 80\% success participants can distinguish a different voice from a familiar voice
    \item Their morphed attack was overall just above 50\% however, their reordering attack had almost 80\% success rate
    \item Both attacks were above the baseline of a different voice. I.e. the case of Mallory just replacing the audio with their voice.
\end{itemize}
